---
title: "Data Visualization - Mini-Project 1"
author: "Scott Shriver `sshriver2380@floridapoly.edu`"
output: html_notebook
---

We will start by loading in the Minnesota I-94 data, then checking the first few rows and getting an overall data summary

```{r}
library(tidyverse)
minnesota <- read.csv("https://raw.githubusercontent.com/reisanar/datasets/master/trafficMN.csv")
head(minnesota)
```

```{r}
summary(minnesota)
```

## Weather and Traffic Volume

```{r}
ggplot(data = minnesota) +
  geom_col(aes(x = weather_main, y = traffic_volume)) +
  labs(x = "Main weather event",
       y = "Volume of traffic")
```

## Cloud Coverage and Traffic Volume

Want to see if cloud coverage has any impact of volume of traffic.
Create a smooth line to try and help visualize relation.

```{r}
ggplot(data = minnesota,
       mapping = aes(x = clouds_all,
                     y = traffic_volume)) +
  geom_line() +
  geom_smooth() +
  labs(x = "Percentage cloud coverage",
       y = "Volume of traffic")
```

Overall, volume seems fairly consistent.

## Amount of Snow and Traffic Volume

Want to see relation between amount of snow and traffic volume.
Number of data points collected during hours with no snow means that the "0.0" mark on the x-axis is just a solid vertical line, am limiting the x-axis to focus on hours which had measurable snow.

```{r}
ggplot(data = minnesota) +
  geom_point(aes(x = snow_1h, y = traffic_volume)) +
  coord_cartesian(xlim = c(0.2, 0.6)) +
  labs(x = "Amount of snow in an hour (mm)",
       y = "Volume of traffic")
```

